Full Title of Article\titlebreak This Title Has A Line Break

### 2021-08-30 Submission/Paper/ML4H/Paper.tex
8/29 changes

@@

\paragraph{Annotations}
\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling. As the manual annotation of 279,000+ sequences in not feasible, we devised a scheme to expedite annotations known as "always patterns". An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e. yes, no, or neither). If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly. Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually. % {Will change} %

@@

\label{sec:Transformer}  
\paragraph{(3)Transformer Based Sequence Classification Language Model} % {To be implemented} %

>>>>

 \let\SUP\textsuperscript

@@

\paragraph{Annotations}
\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling. In order to expedite annotations, we devised a scheme to known as "always patterns". An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e. yes, no, or neither). If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly. Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually. % {Will change} %

@@

\label{sec:Transformer}  
\paragraph{(3) Transformer Based Sequence Classification Language Model} % {To be implemented} %
